Evolution, functional diversity, regime shifts, hysteresis, and nonlinearity; ecosystem responses to environmental change.

### 2021-06-18 manuscript/article.Rmd
new sims added

```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
#ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad1_old_strain_var.RDS"))
ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad_new2.RDS"))
ss_novar <- ss_sim_data[1,]
p1  <- plot_ss_result1(ss_novar$ss_res[[1]],
                ss_novar$CB_var_gmax_s,
                ss_novar$CB_var_h_s,
                ss_novar$SB_var_gmax_s,
                ss_novar$SB_var_h_s,
                ss_novar$PB_var_gmax_s,
                ss_novar$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1

>>>>

```{r ss_novar, out.width="1\\linewidth", include=TRUE, fig.align="center", fig.cap=c("your caption"), echo=FALSE}
#ss_sim_data <- readRDS(here("simulations/sim data/ss_res_grad1_old_strain_var.RDS"))
ss_sim_data <- readRDS(here("simulations/sim data/ss_res_CBSBPB_var.RDS"))
ss_novar <- ss_sim_data[1,]
p1  <- plot_ss_result1(ss_novar$ss_res[[1]],
                ss_novar$CB_var_gmax_s,
                ss_novar$CB_var_h_s,
                ss_novar$SB_var_gmax_s,
                ss_novar$SB_var_h_s,
                ss_novar$PB_var_gmax_s,
                ss_novar$PB_var_h_s,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1
